### 2024-02-26 ms.qmd
Updates

Here, we studied the interactive contribution of prenatal temperature and CORT on behavioural flexibility in two species that exhibit distinct outcomes in their roles as invasive species, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L. guichenoti_). These two species are closely related and share similar life history traits [@chapple_know_2011; @chapple_biology_2014], but only _L. delicata_ has successfully colonised different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI]. Some studies have shown differences in personality traits between these two species that can be related to higher behavioural flexibility in _L. delicata_, and are likely key to its invasive success [@chapple_know_2011; @chapple2012can; @bezzina2014does]. However, differences between species in behavioural flexibility and how this trait is affected by the prenatal environment remain unknown. To investigate these effects, we first manipulated CORT levels and incubation temperature in eggs from both species, then subjected the juveniles to a reversal learning task to measure behavioural flexibility [@brown2010behavioral; @szabo2020can]. We predicted that _L. delicata_ would, on average, perform more proficiently in the task than _L. guichenoti_. We also predicted that prenatal CORT and temperature would affect the behavioural flexibility of both species and that _L. guichenoti_ would be more impacted by the prenatal treatments than _L. delicata_. **The rationale behind this prediction is that behavioural flexibility is expected to be preserved through generations in invassive species, and as such, less impacted by early environment.** Further, we predicted those incubated at higher temperatures to perform better in the reversal task because high prenatal temperatures often improve performance in cognitive tasks in ectotherms [@amiel_hotter_2012; @amiel_egg_2014; @clark_colour_2014]. Conversely, we predicted that prenatal CORT would impair learning as shown in other species [@lemaire_prenatal_2000; @zhu_prenatal_2004; @lui2017chronic]. Finally, we expected an interaction between both treatments, with high temperatures mitigating the negative effects of prenatal CORT on the performance of the lizards in the task. This may occur for two reasons that are not mutually exclusive: first, an increase in temperature leads to an overall rise in neural density [@amiel_effects_2017], thereby counteracting the impact of CORT [see @lemaire_prenatal_2000; @zhu_prenatal_2004]; and second, the elevated metabolic rate associated with higher temperatures accelerates the metabolism of CORT, resulting in embryos being exposed to CORT for a shorter time.

@@

@@

@@

>>>>

Here, we studied the interactive effects of prenatal temperature and CORT on behavioural flexibility in two species with distinct histories of invasiveness, the delicate skink (_Lampropholis delicata_) and the common garden skink (_L. guichenoti_). _L. delicata_ has been succesful in colonising different areas around the globe [@baker1979rainbow; @chapple2013divergent; @chapple2015deliinvLHI], but the same is not true of _L. guichenoti_ despite the two species having similar life-histories and overlapping distributions [@chapple_know_2011; @chapple_biology_2014]. Personality has been shown to be different between these two species [@chapple_know_2011; @chapple2012can; @bezzina2014does], which could be related to general cognitive differences that are important for invasion success. Additionally, early environments are known to affect suites of morphological and behavioural traits differently in each species [**REFS**], but the interactive role of maternal CORT and early temperatures have not yet been explored. Differences in the relative impact that early environments have on behavioural flexibility may help explain differing invasion success between the two species. We predicted that _L. delicata_ would, on average, perform more proficiently in the task compared to _L. guichenoti_. We also anticipated prenatal CORT and temperature to affect the behavioural flexibility of both species, and that _L. guichenoti_ would be more impacted by the prenatal environment than _L. delicata_.

@@

# Estimate total sample size per species and number of observations (this will allow to include this data in the first column of the table)
n_deli <- n_list$delicata_CORT_Cold+n_list$delicata_Control_Cold+n_list$delicata_CORT_Hot+n_list$delicata_Control_Hot
ob_deli <- sum(clean_df$species == "delicata", na.rm = TRUE)
n_guich <- n_list$guichenoti_CORT_Cold+n_list$guichenoti_Control_Cold+n_list$guichenoti_CORT_Hot+n_list$guichenoti_Control_Hot
ob_guich <- sum(clean_df$species == "guichenoti", na.rm = TRUE)

@@

    italic(i= c(1, 5), j = 1, italic = TRUE, part = "body") %>% # To have names of species in italics

@@

    flextable::compose(i = 2, j = 1, value = as_paragraph(sprintf("N = %d", n_deli)), part = "body") %>% # To write the delicata sample size
    flextable::compose(i = 6, j = 1, value = as_paragraph(sprintf("N = %d", n_guich)), part = "body") %>% # To write the guichenoti sample size
    flextable::compose(i = 3, j = 1, value = as_paragraph(sprintf("Obs = %d", ob_deli)), part = "body") %>% # To write the delicata total observations
    flextable::compose(i = 7, j = 1, value = as_paragraph(sprintf("Obs = %d", ob_guich)), part = "body") %>% # To write the guichenoti total observations
